Dynamic Transition Analysis with TIMES

### 2020-06-23 doc/2020-03-paper/acks.tex
section 3 added parameter details, added section 5 notes
Former-commit-id: 3c3e5fdaddb8f4d18f3fe5b84bec77119d161dcf
Former-commit-id: fd5392759009fc1b04c95f5123799685cb74ee9b

The authors contributed to this work as described below.

Kathryn D. Huff supervised the work, conceived and contributed to conception of the simulations, and reviewed drafts of the paper.  Prof. Huff is supported by the Nuclear Regulatory Commission Faculty Development Program, the National Center for Supercomputing Applications, the International Institute for Carbon Neutral Energy Research (WPI-I2CNER), 
sponsored by the Japanese Ministry of Education, Culture, Sports, Science and Technology, and  DOE ARPA-E MEITNER program award DE-AR0000983.

>>>>

%The authors contributed to this work as described below.
%
%
%Kathryn D. Huff supervised the work, conceived and contributed to conception of the simulations, and reviewed drafts of the paper.  Prof. Huff is supported by the Nuclear Regulatory Commission Faculty Development Program, the National Center for Supercomputing Applications, the International Institute for Carbon Neutral Energy Research (WPI-I2CNER), 
%sponsored by the Japanese Ministry of Education, Culture, Sports, Science and Technology, and  DOE ARPA-E MEITNER program award DE-AR0000983.

### 2020-06-23 doc/2020-03-paper/conclusion.tex
updates to section 3
Former-commit-id: 75b8a4e4d2f916c3fbd93ac61343e53675edb58a
Former-commit-id: 89fa8262a5e8ce794da5c196f7937e9ad3251205
section 3 added parameter details, added section 5 notes
Former-commit-id: 3c3e5fdaddb8f4d18f3fe5b84bec77119d161dcf
Former-commit-id: fd5392759009fc1b04c95f5123799685cb74ee9b

\section{Conclusion} \label{Conclusion}
Conclusion
\section{Future work}
FUTURE WORK

@@

NECESARY?

>>>>

\section{Conclusion} \label{Conclusion}
Notes for Ansh:
Importance of nuclear : cost of various transitions, flexibility by itself and when coupled with storage (Li-ion, H2). How it precludes the need for CCS.
Urgency of transition : scenarios + sensitivity analysis.
Li-ion storage: land use requirements for each case, qualitatively discuss Co, Ni requirements.
AECs,PEMECs,SOECs need to be highly flexible with high availability factors.
SOFCs: need for extremely responsive SOFCs with high availability factor, flexible operation (cite challenges from NREL).
\section{Future work}

@@

### 2020-06-23 doc/2020-03-paper/methods.tex
section 3 added parameter details, added section 5 notes
Former-commit-id: 3c3e5fdaddb8f4d18f3fe5b84bec77119d161dcf
Former-commit-id: fd5392759009fc1b04c95f5123799685cb74ee9b

To explore possible pathways to curbing \gls{GHG} emissions, we simulated different transition scenarios with different combinations of technologies enabled for deployment. The first set of technologies includes conventional technologies such as  \gls{USC},\gls{lng}, solar photovoltaic, wind energy (with onshore, offshore-fixed and offshore-floating considered separately) and utility-scale lithium-ion battery storage. New deployments of oil-fuelled power plants are disabled due to the declining use of oil for electricity generation in Japan, as it is contrary to Japan's goal of energy security and independence under the Basic Energy Plan. The second set of technologies considered includes emerging carbon-neutral technologies, namely \gls{CCS} and utility-scale hydrogen power. Based on their technological readiness and scalability, \gls{CCS}-based coal and natural gas,\gls{AEC},\gls{PEMEC},\gls{PEMFC}, and \gls{SOFC} were selected for simulation. It is also important to consider the impact of nuclear energy as it has extremely low life-cycle emissions and a high capacity factor,thereby being more reliable than renewables. However, nuclear power faces extremely low public acceptance in Japan after the Fukushima Daiichi accident, and its future in Japan is highly uncertain. Hence, scenarios where new nuclear reactor deployment is enabled and disabled must be juxtaposed to assess the potential role of nuclear in decarbonization of the electricity generation sector. Finally, the long-term impact of nascent technologies on the hydrogen economy is considered in an additional scenario. In this scenario, the potential of the commercialization of \gls{SOEC} and \gls{PWS} post-2050 is explored. Thus, five scenarios are simulated to explore possible transition pathways under the aforementioned conditions, and these are detailed in table \ref{scen-table}.

ADD TECH PARAMS,ASSUMPTIONS, FIX TABLE.
The economic data, emission coefficients, nameplate capacity limits and growth rates incorporated in the model are detailed in tables \ref{eco}, \ref{caplim}, and \ref{growrate} respectively.

>>>>

To explore possible pathways to curbing \gls{GHG} emissions, we simulated different transition scenarios with different combinations of technologies enabled for deployment. The first set of technologies includes conventional technologies such as  \gls{USC},\gls{lng}, solar photovoltaic, wind energy (with onshore, offshore-fixed and offshore-floating considered separately) and utility-scale lithium-ion battery storage. New deployments of oil-fuelled power plants are not considered due to the declining use of oil for electricity generation in Japan, as it is contrary to Japan's goal of energy security and independence as per the Basic Energy Plan. The second set of technologies considered includes emerging carbon-neutral technologies that are already commercialized or close to commercialization, namely emerging solar photovoltaic (representative of technologies such as perovskites, CdTe),\gls{CCS} and utility-scale hydrogen power. For hydrogen power, steam reforming, steam reforming with \gls{CCS}, \gls{AEC},\gls{PEMEC},\gls{PEMFC}, and \gls{SOFC} were selected for simulation based on their technological. Along with these two technology groups, it is also important to consider the impact of nuclear energy as it has extremely low life-cycle emissions and a high capacity factor,thereby being more reliable than renewables. However, nuclear power faces extremely low public acceptance in Japan after the Fukushima Daiichi accident, and its future in Japan is highly uncertain. Hence, scenarios where new nuclear reactor deployment is enabled and disabled must be juxtaposed to assess the potential role of nuclear in decarbonization of the electricity generation sector. Finally, the long-term impact of nascent hydrogen technologies on the hydrogen economy is assessed in an additional scenario. In this scenario, the potential commercialization of \gls{SOEC} and \gls{PWS} post-2050 is explored. Thus, five scenarios are simulated to explore possible transition pathways under a wide variety of conditions, and these are detailed in table \ref{scen-table}.

The economic data, emission coefficients, nameplate capacity limits and growth rates incorporated in the model are detailed in tables \ref{eco}, \ref{caplim}, and \ref{growrate} respectively. Learning curves for costs and life-cycle emissions are compiled from existing data about cost projections, scale-up of manufacturing, availability of manufacturing materials (especially rare earth materials) and the use of clean energy for manufacturing. These learning curves modelled as linear functions interpolated between the data values used, with the curve plateauing at the latest value for said parameter, as detailed in table \ref{eco}. Capacity limits on renewables and \gls{PWS} are based on their land-use requirements, whereas the assumed capacity limits for nuclear are based on the minimum requirement for nuclear in different scenarios. The land use footprint of other technologies is considered negligible. Maximum annual capacity growth rates for existing technologies are constant. The growth rate of nuclear power based on historic trends and current pressure vessel manufacturing limitations. The reactor size assumed in this study is 1165 MWe. The growth rates of all emerging technologies are modeled on the growth rates observed for solar photovoltaic technology, with rapid initial growth plateauing at a moderate maximum growth rate. One notable exception is the maximum growth rate of emerging solar technologies, which we have assumed to be the same as that of existing solar photovoltaic technologies. We believe that these technologies, some of which are already commercialized or close to commercialization,  will benefit immensely from the already streamlined solar photovoltaic manufacturing and supply chain. Hence they could be deployed as rapidly as solar photovoltaic.
